The GALEX View of ``Boyajian's Star''

### 2017-08-30 paper/paper.tex
add blackbody calc, and author affils

\author{
	James R. A. Davenport\altaffilmark{1,2},
	Kevin R. Covey\altaffilmark{1},
	Riley W. Clarke\altaffilmark{1}, \\
	Zachery Laycock\altaffilmark{1},
	Scott W. Flemming\altaffilmark{3},
	Tabetha S. Boyajian\altaffilmark{4},
	Benjamin T. Montet\altaffilmark{5},\\
	Bernie Shiao\altaffilmark{3},
	Chase C. Million\altaffilmark{6},
	David J. Wilson\altaffilmark{7},
	Manuel Olmedo\altaffilmark{8},
	Eric E. Mamajek\altaffilmark{9}
	}

\altaffiltext{1}{Department of Physics \& Astronomy, Western Washington University, 516 High St., Bellingham, WA 98225, USA}
\altaffiltext{2}{NSF Astronomy and Astrophysics Postdoctoral Fellow}

@@

Analysis of archival optical photographic plates has found that KIC 8462852 may have additionally faded nearly 16\% over the past century \citep{schaefer2016}. Such a precise measurement for a single star is difficult, and the result has been debated \citep{hippke2016}. However, using the 53 ``Full Frame Images'' (FFIs) spread over the 4-year \Kepler mission, \citet{montet2016} were able to trace the brightness of KIC 8462852 using an independent flux calibration. The resulting flux-calibrated FFI light curve showed definitively that KIC 8462852 faded by more than 3\% over 4 years. This long timescale variability has recently been confirmed with an analysis of archival ground-based optical photometry (Simon et al. 2017 in prep).

@@

%%%%%
\begin{figure}[!t]
\centering
\includegraphics[width=2.7in]{KIC8462852_0_lc}
\includegraphics[width=2.7in]{KIC8462852_1_lc}
\includegraphics[width=2.7in]{KIC8462852_2_lc}
\includegraphics[width=2.7in]{KIC8462852_3_lc}
\caption{
Light curves from {\tt gPhoton} sampled at a 20-second cadence for the 4 visits in 2012. All epochs are shown (grey), while those having no photometric warning flags set are highlight (blue). Error bars shown are the photometric errors for each point computed by {\tt gPhoton}.}
\label{fig:shorttime}
\end{figure}

@@

Within each of the four GALEX visits available for KIC 8462852, we searched for short timescale variability using {\tt gPhoton}. While nano-second optical variability has been investigated for this target \citep{abeysekara2016}, few other studies have looked at variability on timescales shorter than the 30-minute cadence available with \Kepler.
The four GALEX visits in 2011 ranged from $\sim$70 to $\sim$1400 seconds in duration. Data for each visit was sampled at a 20 second cadence, as shown in Figure \ref{fig:shorttime}. Small amplitude variability is apparent in several of the visits, with coherent structure over durations of approximately 60-100 seconds. Computing a Lomb-Scargle periodogram using {\tt gatspy} \citep{gatspy}, we find moderate power with a broad peak at around 80-seconds. This appears to be due to the $\sim$120 second observing cycle of the GALEX instrument in the standard ``Petal Pattern'' observing mode, and we believe is not astrophysically significant.
A periodic signal of 0.88 days was found in \Kepler, which was presumed by \citet{boyajian2015} to be due to the rotation of starspots in- and out-of view on the surface of KIC 8462852. However, the four GALEX visits shown in Figure \ref{fig:shorttime} are too short to capture this rotation signature, and thus our GALEX data are not able to explore variability at this timescale.

Since the standard GALEX data for this target was spread over four separate visits, we also examined the medium-timescale variability over $\sim$70 days. In Figure \ref{fig:medtime} we show the median flux from within each of the {\tt gPhoton}-processed visits. The uncertainties shown in Figure \ref{fig:medtime} are computed as the standard deviation in the 20-sec sampled data within each visit, and are $\sim$10x larger than the statistical error on each visit's median flux. Unfortunately this 70-day time window did not correspond to any of the previously identified dimming events from \citet{boyajian2015}. Though there is scatter between these four visits in Figure \ref{fig:medtime}, no significant coherent variability is seen on this intermediate timescale with GALEX.

%%%%%
\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{KIC8462852}
\caption{Median flux within each of the four visits spaced over $\sim$70 days in 2011 by GALEX. Uncertainties shown are the standard deviation in flux within each 20-sec sampled {\tt gPhoton} light curves from Figure \ref{fig:shorttime}. No significant change in flux is seen over this 70 day window.
}
\label{fig:medtime}
\end{figure}

@@

@@

>>>>

\author{
	James R. A. Davenport\altaffilmark{1,2},
	Kevin R. Covey\altaffilmark{1},
	Riley W. Clarke\altaffilmark{1}, \\
	Zachery Laycock\altaffilmark{1},
	Scott W. Fleming\altaffilmark{3},
	Tabetha S. Boyajian\altaffilmark{4},
	Benjamin T. Montet\altaffilmark{5,6},\\
	Bernie Shiao\altaffilmark{3},
	Chase C. Million\altaffilmark{7},
	David J. Wilson\altaffilmark{8},
	Manuel Olmedo\altaffilmark{9},
	Eric E. Mamajek\altaffilmark{10,11}
	}

\altaffiltext{1}{Department of Physics \& Astronomy, Western Washington University, 516 High St., Bellingham, WA 98225, USA}
\altaffiltext{2}{NSF Astronomy and Astrophysics Postdoctoral Fellow}
\altaffiltext{3}{STScI, 3700 San Martin Dr., Baltimore, MD 21218}
\altaffiltext{4}{Department of Physics and Astronomy, Louisiana State University, 261-A Nicholson Hall, Tower Dr, Baton Rouge, LA 70803}
\altaffiltext{5}{Department of Astronomy and Astrophysics, University of Chicago, 5640 S. Ellis Ave, Chicago, IL 60637, USA}
\altaffiltext{6}{NASA Sagan Fellow}
\altaffiltext{7}{Million Concepts LLC, PO Box 119, 141 Mary St, Lemont, PA 16851, USA}
\altaffiltext{8}{Department of Physics, University of Warwick, Coventry CV4 7AL, UK}
\altaffiltext{9}{Instituto Nacional de Astrof\'{i}sica Optica y Electr\'{o}nica, Tonantzintla, Puebla, M\'{e}xico}
\altaffiltext{10}{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Pasadena, CA 91109, USA}
\altaffiltext{11}{Department of Physics \& Astronomy, University of Rochester, Rochester, NY 14627, USA}

@@

Analysis of archival optical photographic plates has found that KIC 8462852 may have additionally faded nearly 16\% over the past century \citep{schaefer2016}. Such a precise measurement for a single star is difficult, and the result has been debated \citep{hippke2016}. However, using the 53 ``Full Frame Images'' (FFIs) spread over the 4-year \Kepler mission, \citet{montet2016} were able to trace the brightness of KIC 8462852 using an independent flux calibration. The resulting flux-calibrated FFI light curve showed definitively that KIC 8462852 faded by more than 3\% over 4 years. A years-long timescale variability, with possible periodicity, has recently been confirmed with an analysis of archival ground-based optical photometry \citep{simon2017}.

@@

%%%%%
\begin{figure}[!t]
\centering
\includegraphics[width=2.7in]{KIC8462852_0_lc}
\includegraphics[width=2.7in]{KIC8462852_1_lc}
\includegraphics[width=2.7in]{KIC8462852_2_lc}
\includegraphics[width=2.7in]{KIC8462852_3_lc}
\caption{
Light curves from {\tt gPhoton} sampled at a 10-second cadence for the 4 visits in 2012. All epochs are shown (grey), while those having no photometric warning flags set are highlight (blue). Error bars shown are the photometric errors for each point computed by {\tt gPhoton}.}
\label{fig:shorttime}
\end{figure}

@@

Within each of the four GALEX visits available for KIC 8462852, we searched for short timescale variability using {\tt gPhoton}. While nano-second optical variability has been investigated for this target \citep{abeysekara2016}, few other studies have looked at variability on timescales shorter than the 30-minute cadence available with \Kepler.
The four GALEX visits in 2011 ranged from $\sim$70 to $\sim$1400 seconds in duration. Data for each visit was sampled at a 10-second cadence, as shown in Figure \ref{fig:shorttime}. Small amplitude variability is apparent in several of the visits, with coherent structure over durations of approximately 60-100 seconds. Computing a Lomb-Scargle periodogram using {\tt gatspy} \citep{gatspy}, we find moderate power with a broad peak at around 80-seconds. This appears to be due to the $\sim$120 second observing cycle of the GALEX instrument in the standard ``Petal Pattern'' observing mode, and we believe is not astrophysically significant.
A periodic signal of 0.88 days was found in \Kepler, which was presumed by \citet{boyajian2015} to be due to the rotation of starspots in- and out-of view on the surface of KIC 8462852. However, the four GALEX visits shown in Figure \ref{fig:shorttime} are too short to capture this rotation signature, and thus our GALEX data are not able to explore variability at this timescale.

Since the standard GALEX data for this target was spread over four separate visits, we also examined the medium-timescale variability over $\sim$70 days. In Figure \ref{fig:medtime} we show the median flux from within each of the {\tt gPhoton}-processed visits. The uncertainties shown in Figure \ref{fig:medtime} are computed as the standard deviation in the 10-sec sampled data within each visit, and are $\sim$10x larger than the statistical error on each visit's median flux. Unfortunately this 70-day time window did not correspond to any of the previously identified dimming events from \citet{boyajian2015}. Though there is scatter between these four visits in Figure \ref{fig:medtime}, no significant coherent variability is seen on this intermediate timescale with GALEX.

%%%%%
\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{KIC8462852}
\caption{Median flux within each of the four visits spaced over $\sim$70 days in 2011 by GALEX. Uncertainties shown are the standard deviation in flux within each 10-sec sampled {\tt gPhoton} light curves from Figure \ref{fig:shorttime}. No significant change in flux is seen over this 70 day window.
}
\label{fig:medtime}
\end{figure}

@@

new papers: \citep{meng2017} (new extinction, confirms our Rv), simon2017 (no long-term effect, but confirms slow fading over this timescale), %rappaport2017 (exocomets may explain short timescale dips)

@@

Work by B.T.M. was performed under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.

DJW has received funding from the European Research Council under the European Union’s Seventh Framework Programme (FP/2007-2013)/ERC Grant Agreement n. 320964 (WDTracer).

Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of Technology. under a contract with the National Aeronautics and Space Administration. This document does not contain export controlled information.
